XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-25 talk/icooolps2011/code/interpreter-slow.tex
- simplify the code a bit - delete the .py files now that the tex files are not generated any more

\begin{lstlisting}[mathescape,basicstyle=\ttfamily]
class Class(object):
    def __init__(self, name):
        self.name = name
        self.methods = {}

@@

    def find_method(self, name):
        result = self.methods.get(name)
        if result is not None:
            return result
        raise AttributeError(name)

@@

    def getfield(self, name):
        result = self.attributes.get(name)
        if result is not None:
            return result
        raise AttributeError(name)

@@

    def getattr(self, name):
        try:
            return self.getfield(name)
        except AttributeError:
            return self.cls.find_method(name)
\end{lstlisting}

>>>>

\begin{lstlisting}[mathescape,basicstyle=\ttfamily,numbers = right]
class Class(object):
    def __init__(self, name):
        self.name = name
        self.methods = {}

@@

    def find_method(self, name):
        return self.methods.get(name, None)

@@

    def getfield(self, name):
        return self.attributes.get(name, None)

@@

    def getattr(self, name):
	result = self.getfield(name)
	if result is None:
            result = self.cls.find_method(name)
	    if result is None:
		raise AttributeError
\end{lstlisting}

### 2011-03-25 talk/icooolps2011/code/map.tex
- simplify the code a bit - delete the .py files now that the tex files are not generated any more

    def getfield(self, name):
        map = hint(self.map, promote=True)
        index = map.getindex(name)
        if index != -1:
            return self.storage[index]
        raise AttributeError(name)

@@

    def getattr(self, name):
        try:
            return self.getfield(name)
        except AttributeError:
            return self.cls.find_method(name)
\end{lstlisting}

>>>>

    def getfield(self, name):
        map = hint(self.map, promote=True)
        index = map.getindex(name)
        if index != -1:
            return self.storage[index]
        return None

@@

    def getattr(self, name):
	... # as before
\end{lstlisting}

### 2011-03-25 talk/icooolps2011/code/version.tex
- simplify the code a bit - delete the .py files now that the tex files are not generated any more

    def find_method(self, name):
        self = hint(self, promote=True)
        version = hint(self.version, promote=True)
        result = self._find_method(name, version)
        if result is not None:
            return result
        raise AttributeError(name)

>>>>

    def find_method(self, name):
        self = hint(self, promote=True)
        version = hint(self.version, promote=True)
        return self._find_method(name, version)
